Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies

### 2023-05-30 Tables/mdlTheory.tex
robustness re-render

\hspace{1em}(Intercept) & 74.28**** [70.20, 78.36] &  & 72.53**** [66.81, 78.26] &  & 72.50**** [66.74, 78.25] &  & 78.84**** [76.86, 80.83] &  & 70.71**** [67.55, 73.87] &  & 70.67**** [67.50, 73.84] &  & 81.36**** [78.53, 84.19] &  & 68.32**** [65.10, 71.54] &  & 68.32**** [65.09, 71.54] &  & 81.42**** [78.57, 84.26] &  & 68.36**** [65.16, 71.56] &  & 68.34**** [65.12, 71.56] &  & 68.33**** [65.05, 71.61] & \\
\hspace{1em}CoreNeed & 0.42**** [ 0.32,  0.52] & 0.40 [0.31, 0.49] & 0.17** [ 0.06,  0.29] & 0.30 [0.18, 0.41] & 0.04 [-0.08,  0.15] & 0.13 [0.00, 0.26] & 0.40**** [ 0.28,  0.52] & 0.27 [0.18, 0.37] & 0.13*** [ 0.07,  0.19] & 0.14 [0.06, 0.22] & 0.03 [-0.01,  0.07] & 0.07 [-0.01, 0.15] & 0.43**** [ 0.33,  0.54] & 0.31 [0.24, 0.38] & 0.19**** [ 0.12,  0.27] & 0.18 [0.11, 0.24] & 0.11** [ 0.05,  0.17] & 0.10 [0.04, 0.16] &  &  &  &  &  &  & 0.13**** [ 0.08,  0.17] & 0.12 [0.05, 0.18]\\
\hspace{1em}Quality &  &  &  &  & 0.23*** [ 0.12,  0.33] & 0.41 [0.29, 0.54] &  &  &  &  & 0.17**** [ 0.11,  0.23] & 0.24 [ 0.14, 0.34] &  &  &  &  & 0.17**** [ 0.12,  0.22] & 0.23 [0.17, 0.30] &  &  &  &  & 0.17**** [ 0.12,  0.23] & 0.22 [0.15, 0.29] &  & \\
\hspace{1em}Allport &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 0.65**** [ 0.54,  0.76] & 0.46 [0.39, 0.52] & 0.22**** [ 0.15,  0.29] & 0.21 [0.14, 0.27] & 0.09** [ 0.03,  0.15] & 0.10 [0.03, 0.16] & 0.17*** [ 0.09,  0.24] & 0.17 [0.11, 0.23]\\

@@

\hspace{1em}$\sigma^2$ & 261.1 &  & 63.08 &  & 37.6 &  & 275.7 &  & 89.83 &  & 76.47 &  & 222.5 &  & 91.84 &  & 82.15 &  & 188.9 &  & 93.05 &  & 83.82 &  & 90.78 & \\
\hspace{1em}$\tau_{00}$ & 71.13 (PID) &  & 173.49 (PID) &  & 177.88 (PID) &  & 63.00 (PID) &  & 259.79 (PID) &  & 264.19 (PID) &  & 131.33 (PID) &  & 182.38 (PID) &  & 183.10 (PID) &  & 134.62 (PID) &  & 179.74 (PID) &  & 182.79 (PID) &  & 189.33 (PID) & \\
\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.05 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.03 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[c]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
\hspace{1em}$\rho_{01}$ &  &  & 0.03 (cor.slope.intercept) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.22 (PID.Quality)} &  & -0.09 (cor.slope.intercept) &  & -0.16 (cor.slope.intercept) &  & \makecell[c]{-0.18 (PID.CoreNeed)\\-0.06 (PID.Quality)} &  & -0.26 (cor.slope.intercept) &  & -0.26 (cor.slope.intercept) &  & \makecell[c]{-0.14 (PID.CoreNeed)\\-0.41 (PID.Quality)} &  & -0.07 (cor.slope.intercept) &  & -0.19 (cor.slope.intercept) &  & \makecell[c]{ 0.12 (PID.Allport)\\-0.51 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\
\hspace{1em}$\rho_{00}$ &  &  &  &  & -0.47 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.79 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.10 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.11 (PID.Allport-Quality) &  & 0.07 (PID.CoreNeed-Allport) & \\

@@

\hspace{1em}AIC & 3294 &  & 2816 &  & 2672 &  & 8073 &  & 7222 &  & 7141 &  & 14054 &  & 12632 &  & 12494 &  & 13805 &  & 12652 &  & 12519 &  & 12625 & \\
\hspace{1em}BIC & 3309 &  & 2839 &  & 2712 &  & 8102 &  & 7251 &  & 7190 &  & 14087 &  & 12665 &  & 12548 &  & 13838 &  & 12684 &  & 12573 &  & 12679 & \\

@@

\hspace{1em}ICC & 0.2141 &  & 0.7458 &  & 0.8404 &  & 0.2547 &  & 0.7471 &  & 0.7835 &  & 0.3933 &  & 0.6738 &  & 0.7006 &  & 0.4433 &  & 0.6679 &  & 0.6963 &  &  & \\
$R^2_{marginal}$ / $R^2_{conditional}$ & 0.117 / 0.306 &  & 0.030 / 0.753 &  & 0.067 / 0.851 &  & 0.102 / 0.331 &  & 0.012 / 0.750 &  & 0.028 / 0.789 &  & 0.070 / 0.436 &  & 0.019 / 0.680 &  & 0.041 / 0.713 &  & 0.149 / 0.526 &  & 0.024 / 0.676 &  & 0.040 / 0.709 &  & 0.086 / NA & \\

>>>>

\hspace{1em}(Intercept) & 67.16**** [62.99, 71.34] &  & 72.53**** [66.81, 78.26] &  & 72.50**** [66.74, 78.26] &  & 67.46**** [65.17, 69.76] &  & 70.71**** [67.55, 73.87] &  & 70.69**** [67.52, 73.85] &  & 72.20**** [68.71, 75.70] &  & 68.32**** [65.10, 71.54] &  & 68.32**** [65.10, 71.54] &  & 72.23**** [68.75, 75.72] &  & 68.36**** [65.16, 71.56] &  & 68.36**** [65.14, 71.58] &  & 68.33**** [65.05, 71.61] & \\
\hspace{1em}CoreNeed & 0.37**** [ 0.28,  0.47] & 0.39 [0.30, 0.48] & 0.17** [ 0.06,  0.29] & 0.30 [0.18, 0.41] & 0.05 [-0.05,  0.14] & 0.12 [0.00, 0.24] & 0.29**** [ 0.19,  0.40] & 0.20 [0.10, 0.31] & 0.13*** [ 0.07,  0.19] & 0.14 [0.06, 0.22] & 0.06* [ 0.01,  0.11] & 0.09 [0.01, 0.17] & 0.45**** [ 0.36,  0.54] & 0.31 [0.24, 0.37] & 0.19**** [ 0.12,  0.27] & 0.18 [0.11, 0.24] & 0.12*** [ 0.06,  0.19] & 0.10 [0.04, 0.16] &  &  &  &  &  &  & 0.13**** [ 0.08,  0.17] & 0.12 [0.05, 0.18]\\
\hspace{1em}Quality &  &  &  &  & 0.24*** [ 0.13,  0.35] & 0.45 [0.31, 0.59] &  &  &  &  & 0.16**** [ 0.11,  0.21] & 0.22 [0.13, 0.30] &  &  &  &  & 0.16**** [ 0.11,  0.20] & 0.24 [0.18, 0.31] &  &  &  &  & 0.16**** [ 0.11,  0.21] & 0.23 [0.16, 0.29] &  & \\
\hspace{1em}Allport &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 0.62**** [ 0.49,  0.74] & 0.40 [0.33, 0.47] & 0.22**** [ 0.15,  0.29] & 0.21 [0.14, 0.27] & 0.11** [ 0.05,  0.18] & 0.11 [0.05, 0.17] & 0.17*** [ 0.09,  0.24] & 0.17 [0.11, 0.23]\\

@@

\hspace{1em}$\sigma^2$ & 224.8 &  & 63.08 &  & 35.4 &  & 267.5 &  & 89.83 &  & 79.34 &  & 230 &  & 91.84 &  & 84.56 &  & 197.5 &  & 93.05 &  & 86.99 &  & 90.78 & \\
\hspace{1em}$\tau_{00}$ & 77.54 (PID) &  & 173.49 (PID) &  & 178.05 (PID) &  & 98.57 (PID) &  & 259.79 (PID) &  & 263.15 (PID) &  & 207.01 (PID) &  & 182.38 (PID) &  & 182.78 (PID) &  & 207.46 (PID) &  & 179.74 (PID) &  & 182.20 (PID) &  & 189.33 (PID) & \\
\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.03 (PID.CoreNeed)\\0.05 (PID.Quality)} &  & 0.07 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[c]{0.01 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.07 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.03 (PID.CoreNeed)\\0.01 (PID.Quality)} &  & 0.17 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[c]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
\hspace{1em}$\rho_{01}$ &  &  & 0.03 (cor.slope.intercept) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.26 (PID.Quality)} &  & 0.27 (cor.slope.intercept) &  & -0.16 (cor.slope.intercept) &  & \makecell[c]{-0.10 (PID.CoreNeed)\\-0.27 (PID.Quality)} &  & 0.06 (cor.slope.intercept) &  & -0.26 (cor.slope.intercept) &  & \makecell[c]{-0.27 (PID.CoreNeed)\\-0.27 (PID.Quality)} &  & 0.24 (cor.slope.intercept) &  & -0.19 (cor.slope.intercept) &  & \makecell[c]{-0.10 (PID.Allport)\\-0.38 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\
\hspace{1em}$\rho_{00}$ &  &  &  &  & -0.34 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.74 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.36 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.09 (PID.Allport-Quality) &  & 0.07 (PID.CoreNeed-Allport) & \\

@@

\hspace{1em}AIC & 3240 &  & 2816 &  & 2651 &  & 8062 &  & 7222 &  & 7158 &  & 14129 &  & 12632 &  & 12538 &  & 13918 &  & 12652 &  & 12576 &  & 12625 & \\
\hspace{1em}BIC & 3255 &  & 2839 &  & 2690 &  & 8091 &  & 7251 &  & 7206 &  & 14161 &  & 12665 &  & 12592 &  & 13950 &  & 12684 &  & 12630 &  & 12679 & \\

@@

\hspace{1em}ICC & 0.2565 &  & 0.7458 &  & 0.8472 &  & 0.3052 &  & 0.7471 &  & 0.7741 &  & 0.485 &  & 0.6738 &  & 0.6943 &  & 0.5399 &  & 0.6679 &  & 0.6863 &  &  & \\
$R^2_{marginal}$ / $R^2_{conditional}$ & 0.103 / 0.333 &  & 0.030 / 0.753 &  & 0.068 / 0.858 &  & 0.054 / 0.343 &  & 0.012 / 0.750 &  & 0.024 / 0.780 &  & 0.063 / 0.517 &  & 0.019 / 0.680 &  & 0.039 / 0.706 &  & 0.111 / 0.591 &  & 0.024 / 0.676 &  & 0.041 / 0.699 &  & 0.086 / NA & \\
